Through the eyes of the teacher - Multimodal exploration of expertise differences

### 2024-09-24 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_09_24_MK.Rmd
expertise

@@

# Boxplot showing outliers
ggplot(df_aoi_sum, aes(x = "", y = Number_fixation_min_mtu)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "Boxplot of number of fixations per minute (micro-teaching unit)",
       y = "Number of fixations per minute") +
  theme_minimal()

# Calculate the IQR and bounds
Q1 <- quantile(df_aoi_sum$Number_fixation_min_mtu, 0.25)
Q3 <- quantile(df_aoi_sum$Number_fixation_min_mtu, 0.75)
IQR <- Q3 - Q1

@@

# Filter to remove outliers
df_no_outliers_mtu <- df_aoi_sum %>%
  filter(Number_fixation_min_mtu >= LowerBound & Number_fixation_min_mtu <= UpperBound)

# Check the number of rows before and after filtering
nrow(df_aoi_sum)  # Original data
nrow(df_no_outliers_mtu)  # After removing outliers

######## N, M, SD, min & max number of fixation per minute (micro-teaching unit)
nof.table <-
  df_aoi_sum %>%
  group_by(Group) %>%
  summarise(
    N = n(),
    "M" = round(mean(Number_fixation_min_mtu), digits = 2),
    "SD" = round(sd(Number_fixation_min_mtu), digits = 2),
    "Min" = round(min(Number_fixation_min_mtu), digits = 2),
    "Max" = round(max(Number_fixation_min_mtu), digits = 2)
  )

@@

# plotting number of fixations (micro-teaching unit)
df_aoi_sum %>%
  ggplot(mapping = aes(x = Group, y = Number_fixation_min_mtu)) +
  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
  geom_point(
    size = 2,
    alpha = 0.7,
    position = position_jitter(
      seed = 1,
      width = 0.1,
      height = 0.1
    )
  ) +
  ylim(0, 150) +
  labs(x = "", y = "Number of fixations per minute") +
  scale_fill_brewer(palette  = "RdBu") +
  ggtitle("Number of fixations per minute\n(micro-teaching unit)") +
  theme_cowplot() +
  theme(legend.position = "none") -> plot_number_group

@@

# NUMBER OF FIXATIONS PER MINUTE (micro-teaching unit) 
# t-test for expertise differences
t.test(
  x = df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Expert"],
  y = df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Novice"],
  var.equal = TRUE
)

# NUMBER OF FIXATIONS PER MINUTE (micro-teaching unit)
# effect size for expertise differences
d_number_all <- CohenD(
  x = df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Expert"],
  y = df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Novice"],
  na.rm = TRUE
)

@@

# filter group & total duration & number fixation (AOI students)
df_aoi %>%
  filter(TOI == "Lesson") %>%
  dplyr::select (
    Group,
    Duration_of_interval,
    Participant,
    "Total_duration_of_fixations.Anna",
    "Total_duration_of_fixations.Bianca",
    "Total_duration_of_fixations.Carl(a)",
    "Number_of_fixations.Anna",
    "Number_of_fixations.Bianca",
    "Number_of_fixations.Carl(a)"
  ) %>%
  rowwise() %>%
  transmute(
    Group = as_factor(Group),
    Duration_of_interval_min = round(Duration_of_interval/60000, digits = 2),
    Duration_of_interval_sec = round(Duration_of_interval/1000, digits = 2),
    Participant = Participant,
    Stud_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
    Stud_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
    Stud_number_fixation_min = round(Stud_number_fixation / Duration_of_interval_min, digits = 2),
    Stud_number_fixation_sec = round(Stud_number_fixation / Duration_of_interval_sec, digits = 2),
    Average_duration_stud = round(Stud_duration_fixation / Stud_number_fixation, digits = 0)
    ) -> df_aoi_stud

@@

# Boxplot showing outliers
ggplot(df_aoi_stud, aes(x = "", y = Stud_number_fixation_min)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "Boxplot of number of fixations per minute (AOI students)",
       y = "Number of fixations per minute") +
  theme_minimal()

# Calculate the IQR and bounds
Q1 <- quantile(df_aoi_stud$Stud_number_fixation_min, 0.25)
Q3 <- quantile(df_aoi_stud$Stud_number_fixation_min, 0.75)
IQR <- Q3 - Q1

@@

# Filter to remove outliers
df_no_outliers_stud <- df_aoi_stud %>%
  filter(Stud_number_fixation_min >= LowerBound & Stud_number_fixation_min <= UpperBound)

# Check the number of rows before and after filtering
nrow(df_aoi_stud)  # Original data
nrow(df_no_outliers_stud)  # After removing outliers

# Create a dataframe with only the outliers
df_outliers_stud <- df_aoi_stud %>%
  filter(Stud_number_fixation_min < LowerBound | Stud_number_fixation_min > UpperBound)

# View the removed outliers
df_outliers_stud

##### N, M, SD, min & max number of fixations per minute (AOI students)
nof.min.stud.table <-
  df_no_outliers_stud %>%
  group_by(Group) %>%
  summarise(
    N = n(),
    "M" = round(mean(Stud_number_fixation_min), digits = 2),
    "SD" = round(sd(Stud_number_fixation_min), digits = 2),
    "Min" = round(min(Stud_number_fixation_min), digits = 2),
    "Max" = round(max(Stud_number_fixation_min), digits = 2)
  )

@@

# plotting number of fixations per minute on AOI Students
df_aoi_stud %>%
  ggplot(mapping = aes(x = Group, y = Stud_number_fixation_min)) +
  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
  geom_point(
    size = 2,
    alpha = 0.7,
    position = position_jitter(
      seed = 1,
      width = 0.1,
      height = 0.005
    )
  ) +
  ylim(0, 80) +
  labs(x = "", y = "Number of fixations per minute") +
  scale_fill_brewer(palette  = "RdBu") +
  ggtitle("Number of fixations per minute\n(AOI students)") +
  theme_cowplot() +
  theme(legend.position = "none") -> plot_number_min_stud

@@

# NUMBER OF FIXATIONS on AOI students 
# t-test for expertise differences
t.test(
  x = df_no_outliers_stud$Stud_number_fixation_min[df_no_outliers_stud$Group == "Expert"],
  y = df_no_outliers_stud$Stud_number_fixation_min[df_no_outliers_stud$Group == "Novice"],
  var.equal = TRUE
)

# NUMBER OF FIXATIONS on AOI students
# effect size for expertise differences
d_number_stud <- CohenD(
  x = df_no_outliers_stud$Stud_number_fixation_min[df_no_outliers_stud$Group == "Expert"],
  y = df_no_outliers_stud$Stud_number_fixation_min[df_no_outliers_stud$Group == "Novice"],
  na.rm = TRUE
)

@@

@@

# Boxplot showing outliers
ggplot(df_aoi_disrup, aes(x = "", y = Number_of_fixations.Disruptive_Person)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "Boxplot of number of fixations per minute (AOI disruptive person)",
       y = "Number of fixations per minute") +
  theme_minimal()

# Calculate the IQR and bounds
Q1 <- quantile(df_aoi_disrup$Number_of_fixations.Disruptive_Person, 0.25)
Q3 <- quantile(df_aoi_disrup$Number_of_fixations.Disruptive_Person, 0.75)
IQR <- Q3 - Q1

@@

# Filter to remove outliers
df_no_outliers_disrup <- df_aoi_disrup %>%
  filter(Number_of_fixations.Disruptive_Person >= LowerBound & Number_of_fixations.Disruptive_Person <= UpperBound)

# Check the number of rows before and after filtering
nrow(df_aoi_disrup)  # Original data
nrow(df_no_outliers_disrup)  # After removing outliers

# Create a dataframe with only the outliers
df_outliers_disrup <- df_aoi_disrup %>%
  filter(Number_of_fixations.Disruptive_Person < LowerBound | Number_of_fixations.Disruptive_Person > UpperBound)

# View the removed outliers
df_outliers_disrup

######## N, M, SD, min & max number of fixation on AOI "disruptive person"
nof.disrup.table <-
  df_no_outliers_disrup %>%
  group_by(Group) %>%
  summarise(
    N = n(),
    "M" = round(mean(Number_of_fixations.Disruptive_Person), digits = 2),
    "SD" = round(sd(Number_of_fixations.Disruptive_Person), digits = 2),
    "Min" = round(min(Number_of_fixations.Disruptive_Person), digits = 2),
    "Max" = round(max(Number_of_fixations.Disruptive_Person), digits = 2)
  )

@@

# plotting average duration on AOI Disruptive person
df_no_outliers_disrup %>%
  ggplot(mapping = aes(x = Group, y = Number_of_fixations.Disruptive_Person)) +
  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
  geom_point(
    size = 2,
    alpha = 0.7,
    position = position_jitter(
      seed = 1,
      width = 0.1,
      height = 0.1
    )
  ) +
  ylim(0, 100) +
  labs(x = "", y = "Number of fixations") +
  scale_fill_brewer(palette  = "RdBu") +
  ggtitle("Number of fixations\n(AOI disruptive person)") +
  theme_cowplot() +
  theme(legend.position = "none") -> plot_number_disrup

@@

# NUMBER OF FIXATIONS on AOI disruptive person 
# t-test for expertise differences
t.test(x = df_no_outliers_disrup$Number_of_fixations.Disruptive_Person[df_no_outliers_disrup$Group == "Expert"],
       y = df_no_outliers_disrup$Number_of_fixations.Disruptive_Person[df_no_outliers_disrup$Group == "Novice"],
       var.equal = TRUE)

@@

# Boxplot showing outliers
ggplot(df_aoi_sum, aes(x = "", y = Average_duration_mtu)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "Boxplot of Average duration of fixations per minute",
       y = "Average duration of fixations per minute") +
  theme_minimal()

@@

# filter group & total duration & number fixation on AOI Students
df_aoi %>%
  filter(TOI == "Lesson") %>%
  dplyr::select (
    Group,
    "Total_duration_of_fixations.Anna",
    "Total_duration_of_fixations.Bianca",
    "Total_duration_of_fixations.Carl(a)",
    "Number_of_fixations.Anna",
    "Number_of_fixations.Bianca",
    "Number_of_fixations.Carl(a)"
  ) %>%
  rowwise() %>%
  transmute(
    Group = Group,
    Stud_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
    Stud_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE)
  ) %>%
  mutate(
    Average_duration_stud = round(Stud_duration_fixation / Stud_number_fixation, digits = 0),
    Group = as_factor(Group)
  ) -> df_aoi_stud

@@

# Boxplot showing outliers
ggplot(df_aoi_stud, aes(x = "", y = Average_duration_stud)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "Boxplot of average duration of fixations (AOI students)",
       y = "Average duration of fixations") +
  theme_minimal()

# Calculate the IQR and bounds
Q1 <- quantile(df_aoi_stud$Average_duration_stud, 0.25)
Q3 <- quantile(df_aoi_stud$Average_duration_stud, 0.75)
IQR <- Q3 - Q1

@@

# Filter to remove outliers
df_no_outliers_stud_dur <- df_aoi_stud %>%
  filter(Average_duration_stud >= LowerBound & Average_duration_stud <= UpperBound)

# Check the number of rows before and after filtering
nrow(df_aoi_stud)  # Original data
nrow(df_no_outliers_stud_dur)  # After removing outliers

# Create a dataframe with only the outliers
df_outliers_stud_dur <- df_aoi_stud %>%
  filter(Average_duration_stud < LowerBound | Average_duration_stud > UpperBound)

# View the removed outliers
df_outliers_stud_dur

######## N, M, SD, min & max average duration of fixations on AOI students
dur.stud.table <-
  df_no_outliers_stud_dur %>%
  group_by(Group) %>%
  summarise(
    N = n(),
    "M in ms" = round(mean(Average_duration_stud), digits = 2),
    "SD in ms" = round(sd(Average_duration_stud), digits = 2),
    "Min in ms" = round(min(Average_duration_stud), digits = 2),
    "Max in ms" = round(max(Average_duration_stud), digits = 2)
  )

@@

# plotting average duration on AOI Students
df_no_outliers_stud_dur %>%
  ggplot(mapping = aes(x = Group, y = Average_duration_stud)) +
  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
  geom_point(
    size = 2,
    alpha = 0.7,
    position = position_jitter(
      seed = 1,
      width = 0.1,
      height = 0.1
    )
  ) +
  ylim(0, 1000) + 
  labs(x ="",
       y = "Milliseconds") + 
  scale_fill_brewer(palette  = "RdBu") + 
  ggtitle("Average duration of fixations\n(AOI students)") +
  theme_cowplot() +
  theme(legend.position="none") -> plot_average_duration_stud

@@

# AVERAGE DURATION OF FIXATIONS on AOI Students 
# t-test for expertise differences
t.test(
  x = df_no_outliers_stud_dur$Average_duration_stud[df_no_outliers_stud_dur$Group == "Expert"],
  y = df_no_outliers_stud_dur$Average_duration_stud[df_no_outliers_stud_dur$Group == "Novice"],
  var.equal = TRUE
)

@@

# Boxplot showing outliers
ggplot(df_aoi_disrup, aes(x = "", y = Average_duration_disrup)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "Boxplot of average duration of fixations (AOI disruptive person)",
       y = "Average duration of fixations") +
  theme_minimal()

>>>>

# filter only for experts
df_aoi_sum_expert <- df_aoi_sum %>% 
  filter(Group == "Expert")

# filter only for novices
df_aoi_sum_novice <- df_aoi_sum %>% 
  filter(Group == "Novice")

@@

### EXPERTS ###

# Boxplot showing outliers for experts
ggplot(df_aoi_sum_expert, aes(x = "", y = Number_fixation_min_mtu)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "Boxplot of number of fixations per minute (micro-teaching unit)",
       y = "Number of fixations per minute") +
  theme_minimal()

# Calculate the IQR and bounds
Q1 <- quantile(df_aoi_sum_expert$Number_fixation_min_mtu, 0.25)
Q3 <- quantile(df_aoi_sum_expert$Number_fixation_min_mtu, 0.75)
IQR <- Q3 - Q1

@@

# Filter to remove outliers
df_no_outliers_mtu_exp <- df_aoi_sum_expert %>%
  filter(Number_fixation_min_mtu >= LowerBound & Number_fixation_min_mtu <= UpperBound)

# Check the number of rows before and after filtering
nrow(df_aoi_sum_expert)  # Original data
nrow(df_no_outliers_mtu_exp)  # After removing outliers

# Create a dataframe with only the outliers
df_outliers_mtu_exp <- df_aoi_sum_expert %>%
  filter(Number_fixation_min_mtu < LowerBound | Number_fixation_min_mtu > UpperBound)

# View the removed outliers
df_outliers_mtu_exp # ID 205

### NOVICES ###

# Boxplot showing outliers for novices
ggplot(df_aoi_sum_novice, aes(x = "", y = Number_fixation_min_mtu)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "Boxplot of number of fixations per minute (micro-teaching unit)",
       y = "Number of fixations per minute") +
  theme_minimal()

# Calculate the IQR and bounds
Q1 <- quantile(df_aoi_sum_novice$Number_fixation_min_mtu, 0.25)
Q3 <- quantile(df_aoi_sum_novice$Number_fixation_min_mtu, 0.75)
IQR <- Q3 - Q1

# Filter to remove outliers
df_no_outliers_mtu_nov <- df_aoi_sum_novice %>%
  filter(Number_fixation_min_mtu >= LowerBound & Number_fixation_min_mtu <= UpperBound)

# Check the number of rows before and after filtering
nrow(df_aoi_sum_novice)  # Original data
nrow(df_no_outliers_mtu_nov)  # After removing outliers

######## N, M, SD, min & max number of fixation per minute (micro-teaching unit)
nof.table <-
  df_aoi_sum %>%
  filter(!Participant == "205") %>% # exclude outlier
  group_by(Group) %>%
  summarise(
    N = n(),
    "M" = round(mean(Number_fixation_min_mtu), digits = 2),
    "SD" = round(sd(Number_fixation_min_mtu), digits = 2),
    "Min" = round(min(Number_fixation_min_mtu), digits = 2),
    "Max" = round(max(Number_fixation_min_mtu), digits = 2)
  )

@@

# plotting number of fixations (micro-teaching unit)
df_aoi_sum %>%
  filter(!Participant == "205") %>% 
  ggplot(mapping = aes(x = Group, y = Number_fixation_min_mtu)) +
  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
  geom_point(
    size = 2,
    alpha = 0.7,
    position = position_jitter(
      seed = 1,
      width = 0.1,
      height = 0.1
    )
  ) +
  ylim(0, 150) +
  labs(x = "", y = "Number of fixations per minute") +
  scale_fill_brewer(palette  = "RdBu") +
  ggtitle("Number of fixations per minute\n(micro-teaching unit)") +
  theme_cowplot() +
  theme(legend.position = "none") -> plot_number_group

@@

# NUMBER OF FIXATIONS PER MINUTE (micro-teaching unit) 
# create data frame without oulier 
df_aoi_sum_no_out <- df_aoi_sum %>% 
  filter(!Participant == "205")

# t-test for expertise differences
t.test(
  x = df_aoi_sum_no_out$Number_fixation_min_mtu[df_aoi_sum_no_out$Group == "Expert"],
  y = df_aoi_sum_no_out$Number_fixation_min_mtu[df_aoi_sum_no_out$Group == "Novice"],
  var.equal = TRUE
)

# NUMBER OF FIXATIONS PER MINUTE (micro-teaching unit)
# effect size for expertise differences
d_number_all <- CohenD(
  x = df_aoi_sum_no_out$Number_fixation_min_mtu[df_aoi_sum_no_out$Group == "Expert"],
  y = df_aoi_sum_no_out$Number_fixation_min_mtu[df_aoi_sum_no_out$Group == "Novice"],
  na.rm = TRUE
)

@@

# filter group & total duration & number fixation (AOI students)
df_aoi %>%
  filter(TOI == "Lesson") %>%
  dplyr::select (
    Group,
    Duration_of_interval,
    Participant,
    "Total_duration_of_fixations.Anna",
    "Total_duration_of_fixations.Bianca",
    "Total_duration_of_fixations.Carl(a)",
    "Number_of_fixations.Anna",
    "Number_of_fixations.Bianca",
    "Number_of_fixations.Carl(a)"
  ) %>%
  rowwise() %>%
  transmute(
    Group = as_factor(Group),
    Participant = Participant,
    Duration_of_interval_min = round(Duration_of_interval/60000, digits = 2),
    Duration_of_interval_sec = round(Duration_of_interval/1000, digits = 2),
    Stud_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
    Stud_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
    Stud_number_fixation_min = round(Stud_number_fixation / Duration_of_interval_min, digits = 2),
    Stud_number_fixation_sec = round(Stud_number_fixation / Duration_of_interval_sec, digits = 2),
    Average_duration_stud = round(Stud_duration_fixation / Stud_number_fixation, digits = 0)
    ) -> df_aoi_stud

# filter only for experts
df_aoi_stud_expert <- df_aoi_stud %>% 
  filter(Group == "Expert")

# filter only for novices
df_aoi_stud_novice <- df_aoi_stud %>% 
  filter(Group == "Novice")

@@

### EXPERTS ###

# Boxplot showing outliers for experts
ggplot(df_aoi_stud_expert, aes(x = "", y = Stud_number_fixation_min)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "Boxplot of number of fixations per minute (AOI students)",
       y = "Number of fixations per minute") +
  theme_minimal()

# Calculate the IQR and bounds
Q1 <- quantile(df_aoi_stud_expert$Stud_number_fixation_min, 0.25)
Q3 <- quantile(df_aoi_stud_expert$Stud_number_fixation_min, 0.75)
IQR <- Q3 - Q1

@@

# Filter to remove outliers
df_no_outliers_stud_exp <- df_aoi_stud_expert %>%
  filter(Stud_number_fixation_min >= LowerBound & Stud_number_fixation_min <= UpperBound)

# Check the number of rows before and after filtering
nrow(df_aoi_stud_expert)  # Original data
nrow(df_no_outliers_stud_exp)  # After removing outliers

# Create a dataframe with only the outliers
df_outliers_stud_exp <- df_aoi_stud_expert %>%
  filter(Stud_number_fixation_min < LowerBound | Stud_number_fixation_min > UpperBound)

# View the removed outliers
df_outliers_stud_exp

### NOVICES ###

# Boxplot showing outliers for novices
ggplot(df_aoi_stud_novice, aes(x = "", y = Stud_number_fixation_min)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "Boxplot of number of fixations per minute (AOI students)",
       y = "Number of fixations per minute") +
  theme_minimal()

# Calculate the IQR and bounds
Q1 <- quantile(df_aoi_stud_novice$Stud_number_fixation_min, 0.25)
Q3 <- quantile(df_aoi_stud_novice$Stud_number_fixation_min, 0.75)
IQR <- Q3 - Q1

# Filter to remove outliers
df_no_outliers_stud_nov <- df_aoi_stud_novice %>%
  filter(Stud_number_fixation_min >= LowerBound & Stud_number_fixation_min <= UpperBound)

# Check the number of rows before and after filtering
nrow(df_aoi_stud_novice)  # Original data
nrow(df_no_outliers_stud_nov)  # After removing outliers

# Create a dataframe with only the outliers
df_outliers_stud_nov <- df_aoi_stud_novice %>%
  filter(Stud_number_fixation_min < LowerBound | Stud_number_fixation_min > UpperBound)

# View the removed outliers
df_outliers_stud_nov

##### N, M, SD, min & max number of fixations per minute (AOI students)
nof.min.stud.table <-
  df_aoi_stud %>%
  filter(!Participant %in% c("205", "236", "241")) %>%
  group_by(Group) %>%
  summarise(
    N = n(),
    "M" = round(mean(Stud_number_fixation_min), digits = 2),
    "SD" = round(sd(Stud_number_fixation_min), digits = 2),
    "Min" = round(min(Stud_number_fixation_min), digits = 2),
    "Max" = round(max(Stud_number_fixation_min), digits = 2)
  )

@@

# plotting number of fixations per minute on AOI Students
df_aoi_stud %>%
  filter(!Participant %in% c("205", "236", "241")) %>%
  ggplot(mapping = aes(x = Group, y = Stud_number_fixation_min)) +
  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
  geom_point(
    size = 2,
    alpha = 0.7,
    position = position_jitter(
      seed = 1,
      width = 0.1,
      height = 0.005
    )
  ) +
  ylim(0, 80) +
  labs(x = "", y = "Number of fixations per minute") +
  scale_fill_brewer(palette  = "RdBu") +
  ggtitle("Number of fixations per minute\n(AOI students)") +
  theme_cowplot() +
  theme(legend.position = "none") -> plot_number_min_stud

@@

# NUMBER OF FIXATIONS on AOI students 
# create data frame without oulier 
df_aoi_stud_no_out <- df_aoi_stud %>% 
  filter(!Participant %in% c("205", "236", "241"))

# t-test for expertise differences
t.test(
  x = df_aoi_stud_no_out$Stud_number_fixation_min[df_aoi_stud_no_out$Group == "Expert"],
  y = df_aoi_stud_no_out$Stud_number_fixation_min[df_aoi_stud_no_out$Group == "Novice"],
  var.equal = TRUE
)

# NUMBER OF FIXATIONS on AOI students
# effect size for expertise differences
d_number_stud <- CohenD(
  x = df_aoi_stud_no_out$Stud_number_fixation_min[df_aoi_stud_no_out$Group == "Expert"],
  y = df_aoi_stud_no_out$Stud_number_fixation_min[df_aoi_stud_no_out$Group == "Novice"],
  na.rm = TRUE
)

@@

# filter only for experts
df_aoi_disrup_expert <- df_aoi_disrup %>% 
  filter(Group == "Expert")

# filter only for novices
df_aoi_disrup_novice <- df_aoi_disrup %>% 
  filter(Group == "Novice")

@@

### EXPERTS ###

# Boxplot showing outliers for experts
ggplot(df_aoi_disrup_expert, aes(x = "", y = Number_of_fixations.Disruptive_Person)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "Boxplot of number of fixations per minute (AOI disruptive person)",
       y = "Number of fixations per minute") +
  theme_minimal()

# Calculate the IQR and bounds
Q1 <- quantile(df_aoi_disrup_expert$Number_of_fixations.Disruptive_Person, 0.25)
Q3 <- quantile(df_aoi_disrup_expert$Number_of_fixations.Disruptive_Person, 0.75)
IQR <- Q3 - Q1

@@

# Filter to remove outliers
df_no_outliers_disrup_exp <- df_aoi_disrup_expert %>%
  filter(Number_of_fixations.Disruptive_Person >= LowerBound & Number_of_fixations.Disruptive_Person <= UpperBound)

# Check the number of rows before and after filtering
nrow(df_aoi_disrup_expert)  # Original data
nrow(df_no_outliers_disrup_exp)  # After removing outliers

# Create a dataframe with only the outliers
df_outliers_disrup_exp <- df_aoi_disrup_expert %>%
  filter(Number_of_fixations.Disruptive_Person < LowerBound | Number_of_fixations.Disruptive_Person > UpperBound)

# View the removed outliers
df_outliers_disrup_exp

### NOVICES ###

# Boxplot showing outliers for novices
ggplot(df_aoi_disrup_novice, aes(x = "", y = Number_of_fixations.Disruptive_Person)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "Boxplot of number of fixations per minute (AOI disruptive person)",
       y = "Number of fixations per minute") +
  theme_minimal()

# Calculate the IQR and bounds
Q1 <- quantile(df_aoi_disrup_novice$Number_of_fixations.Disruptive_Person, 0.25)
Q3 <- quantile(df_aoi_disrup_novice$Number_of_fixations.Disruptive_Person, 0.75)
IQR <- Q3 - Q1

# Filter to remove outliers
df_no_outliers_disrup_nov <- df_aoi_disrup_novice %>%
  filter(Number_of_fixations.Disruptive_Person >= LowerBound & Number_of_fixations.Disruptive_Person <= UpperBound)

# Check the number of rows before and after filtering
nrow(df_aoi_disrup_novice)  # Original data
nrow(df_no_outliers_disrup_nov)  # After removing outliers

# Create a dataframe with only the outliers
df_outliers_disrup_nov <- df_aoi_disrup_novice %>%
  filter(Number_of_fixations.Disruptive_Person < LowerBound | Number_of_fixations.Disruptive_Person > UpperBound)

# View the removed outliers
df_outliers_disrup_nov

######## N, M, SD, min & max number of fixation on AOI "disruptive person"
nof.disrup.table <- df_aoi_disrup %>% 
  filter(!Participant %in% c("207", "226", "101", "108", "116")) %>% 
  group_by(Group) %>%
  summarise(
    N = n(),
    "M" = round(mean(Number_of_fixations.Disruptive_Person), digits = 2),
    "SD" = round(sd(Number_of_fixations.Disruptive_Person), digits = 2),
    "Min" = round(min(Number_of_fixations.Disruptive_Person), digits = 2),
    "Max" = round(max(Number_of_fixations.Disruptive_Person), digits = 2)
  )

@@

# plotting average duration on AOI Disruptive person
df_aoi_disrup %>% 
  filter(!Participant %in% c("207", "226", "101", "108", "116")) %>% 
  ggplot(mapping = aes(x = Group, y = Number_of_fixations.Disruptive_Person)) +
  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
  geom_point(
    size = 2,
    alpha = 0.7,
    position = position_jitter(
      seed = 1,
      width = 0.1,
      height = 0.1
    )
  ) +
  ylim(0, 100) +
  labs(x = "", y = "Number of fixations") +
  scale_fill_brewer(palette  = "RdBu") +
  ggtitle("Number of fixations\n(AOI disruptive person)") +
  theme_cowplot() +
  theme(legend.position = "none") -> plot_number_disrup

@@

# NUMBER OF FIXATIONS on AOI disruptive person
# create data frame without oulier 
df_no_outliers_disrup <- df_aoi_disrup %>% 
  filter(!Participant %in% c("207", "226", "101", "108", "116"))

# t-test for expertise differences
t.test(x = df_no_outliers_disrup$Number_of_fixations.Disruptive_Person[df_no_outliers_disrup$Group == "Expert"],
       y = df_no_outliers_disrup$Number_of_fixations.Disruptive_Person[df_no_outliers_disrup$Group == "Novice"],
       var.equal = TRUE)

@@

### EXPERTS ###

# Boxplot showing outliers for experts
ggplot(df_aoi_sum_expert, aes(x = "", y = Average_duration_mtu)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "Boxplot of Average duration of fixations",
       y = "Average duration of fixations in msec") +
  theme_minimal()

### NOVICES ###

# Boxplot showing outliers for experts
ggplot(df_aoi_sum_novice, aes(x = "", y = Average_duration_mtu)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "Boxplot of Average duration of fixations",
       y = "Average duration of fixations in msec") +
  theme_minimal()

@@

# filter group & total duration & number fixation on AOI Students
df_aoi %>%
  filter(TOI == "Lesson") %>%
  dplyr::select (
    Group,
    Participant,
    "Total_duration_of_fixations.Anna",
    "Total_duration_of_fixations.Bianca",
    "Total_duration_of_fixations.Carl(a)",
    "Number_of_fixations.Anna",
    "Number_of_fixations.Bianca",
    "Number_of_fixations.Carl(a)"
  ) %>%
  rowwise() %>%
  transmute(
    Group = Group,
    Participant = Participant,
    Stud_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
    Stud_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE)
  ) %>%
  mutate(
    Average_duration_stud = round(Stud_duration_fixation / Stud_number_fixation, digits = 0),
    Group = as_factor(Group)
  ) -> df_aoi_stud

# filter only for experts
df_aoi_stud_expert <- df_aoi_stud %>% 
  filter(Group == "Expert")

# filter only for novices
df_aoi_stud_novice <- df_aoi_stud %>% 
  filter(Group == "Novice")

@@

### EXPERTS ###

# Boxplot showing outliers
ggplot(df_aoi_stud_expert, aes(x = "", y = Average_duration_stud)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "EXPERTS: Boxplot of average duration of fixations (AOI students)",
       y = "Average duration of fixations") +
  theme_minimal()

### NOVICES ###

# Boxplot showing outliers
ggplot(df_aoi_stud_novice, aes(x = "", y = Average_duration_stud)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "NOVICES: Boxplot of average duration of fixations (AOI students)",
       y = "Average duration of fixations") +
  theme_minimal()

# Calculate the IQR and bounds
Q1 <- quantile(df_aoi_stud_novice$Average_duration_stud, 0.25)
Q3 <- quantile(df_aoi_stud_novice$Average_duration_stud, 0.75)
IQR <- Q3 - Q1

@@

# Filter to remove outliers
df_no_outliers_stud_dur_nov <- df_aoi_stud_novice %>%
  filter(Average_duration_stud >= LowerBound & Average_duration_stud <= UpperBound)

# Check the number of rows before and after filtering
nrow(df_aoi_stud_novice)  # Original data
nrow(df_no_outliers_stud_dur_nov)  # After removing outliers

# Create a dataframe with only the outliers
df_outliers_dur_stud_nov <- df_aoi_stud_novice %>%
  filter(Average_duration_stud < LowerBound | Average_duration_stud > UpperBound)

# View the removed outliers
df_outliers_dur_stud_nov

######## N, M, SD, min & max average duration of fixations on AOI students
dur.stud.table <-
  df_aoi_stud %>%
  filter(!Participant %in% c("105", "133")) %>% 
  group_by(Group) %>%
  summarise(
    N = n(),
    "M in ms" = round(mean(Average_duration_stud), digits = 2),
    "SD in ms" = round(sd(Average_duration_stud), digits = 2),
    "Min in ms" = round(min(Average_duration_stud), digits = 2),
    "Max in ms" = round(max(Average_duration_stud), digits = 2)
  )

@@

# plotting average duration on AOI Students
df_aoi_stud %>%
  filter(!Participant %in% c("105", "133")) %>% 
  ggplot(mapping = aes(x = Group, y = Average_duration_stud)) +
  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
  geom_point(
    size = 2,
    alpha = 0.7,
    position = position_jitter(
      seed = 1,
      width = 0.1,
      height = 0.1
    )
  ) +
  ylim(0, 1000) + 
  labs(x ="",
       y = "Milliseconds") + 
  scale_fill_brewer(palette  = "RdBu") + 
  ggtitle("Average duration of fixations\n(AOI students)") +
  theme_cowplot() +
  theme(legend.position="none") -> plot_average_duration_stud

@@

# AVERAGE DURATION OF FIXATIONS on AOI Students 
# create data frame without outlier
df_no_outliers_stud_dur <- df_aoi_stud %>%
  filter(!Participant %in% c("105", "133"))

# t-test for expertise differences
t.test(
  x = df_no_outliers_stud_dur$Average_duration_stud[df_no_outliers_stud_dur$Group == "Expert"],
  y = df_no_outliers_stud_dur$Average_duration_stud[df_no_outliers_stud_dur$Group == "Novice"],
  var.equal = TRUE
)

@@

### EXPERTS ###

# Boxplot showing outliers
ggplot(df_aoi_disrup_expert, aes(x = "", y = Average_duration_disrup)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "Boxplot of average duration of fixations (AOI disruptive person)",
       y = "Average duration of fixations") +
  theme_minimal()
